On the validity of the Born approximation for beyond-Gaussian weak lensing observables

### 2017-05-18 Paper/paper.tex
remove color fonts

\begin{abstract}
Accurate forward modeling of weak lensing (WL) observables from cosmological parameters is necessary for upcoming galaxy surveys. Because WL probes structures in the non--linear regime, analytical forward modeling is very challenging, if not impossible. Numerical simulations of WL features rely on ray--tracing through the outputs of $N$--body simulations, which requires knowledge of the gravitational potential and accurate solvers for light ray trajectories. A less accurate procedure, based on the Born approximation, only requires knowledge of the density field, and can be implemented more efficiently and at a lower computational cost. In this work, we use simulations to show that deviations of the Born--approximated convergence power spectrum, skewness and kurtosis from their fully ray--traced counterparts are consistent with the smallest non--trivial $O(\Phi^3)$ post--Born corrections (so-called geodesic and lens-lens terms). Our results imply a cancellation among the larger $O(\Phi^4)$ (and higher order) terms, consistent with previous analytic work. We also find that cosmological parameter bias induced by the Born approximated power spectrum is negligible even for an LSST--like survey, once galaxy shape noise is considered. The same conclusion is not true when considering higher order statistics, such as the $\kappa$ skewness and kurtosis. Using the \ttt{LensTools} software suite, we show that the Born approximation saves a factor of 4 in computing time with respect to the full ray--tracing in reconstructing the convergence.       
\end{abstract}

@@

\caption{CPU time and memory usage benchmarks for the convergence reconstruction operations. The test case we considered consists in a discretization with $N_l=42$ uniformly spaced lenses between the observer and the sources at $z_s=2$, each with a resolution of $4096^2$ pixels. The $\kappa$ field is resolved with $2048^2$ light rays. We show both the runtime for producing a single field of view and the CPU hours needed to perform the reconstruction 1000 times, to mock an LSST--like galaxy survey. Run times do not include the Poisson solution calculation, as this can be recycled to produce multiple field of view realizations. The Poisson solution run time is negligible in the account of the total CPU time needed for the production of $N_r\gg N_l$ field of view realizations.}
\label{tab:benchmarks}

@@

\begin{figure*}
\begin{center}
\includegraphics[scale=0.4]{Figures/csample.eps}
\end{center}
\caption{Sample convergence outputs for one realization of a $(3.5\,{\rm deg})^2$ field, with source galaxies at redshift $z_s=2$. The figure shows the convergence profile (top left), along with the Born approximation residuals (top right), the lens-lens post--Born contribution (bottom left) and the geodesic contribution (bottom right). The images have been smoothed with a Gaussian kernel of size $\theta_G=0.5\,{\rm arcmin}$.  Note the different scales in the bottom panels: the geodesic term (right), is over an order of magnitude larger than the lens--lens term (left), and is comparable in level and detailed structure to the full residual (top right).} 
\label{fig:csample}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics[scale=0.45]{Figures/powerResiduals.eps}
\end{center}
\caption{Contributions at different $\Phi$ orders to the $\kappa$ power spectrum: the left panel shows the auto power spectra $P_{\rm born,born}$ ($O(\Phi^2)$) and $P_{\rm ll},P_{\rm geo}$ ($O(\Phi^4)$). The right panel shows the residuals between the power spectrum of the full ray--traced $\kappa$ field and the one obtained with the Born approximation. For reference, we show the shape noise contributions (black dashed) and the first non--trivial reduced shear corrections to $P^{\kappa\kappa}$(purple), which can be both added to the forward models after the line of sight integration. Gaussian convolution effects with a window of size $\theta_G=0.5\,{\rm arcmin}$ are included. The residuals are compared to the two $O(\Phi^3)$ terms $2P_{\rm born,ll},2P_{\rm born,geo}$. The quantities shown are the ensemble averages over 8192 realizations of $\kappa$ in the fiducial cosmology $\bb{p}_0$.}
\label{fig:psResiduals}
\end{figure*}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.45]{Figures/bias_ngal_convergence_powerSN_s0_nb100.eps}
\end{center}
\caption{Parameter bias, obtained from the $\kappa$ power spectrum, as a function of the galaxy density angular $n_g$ used to compute the shape noise rms in eq. (\ref{par:shaperms}). The plotted quantity is the difference between the mean of 1000 parameter fits using the estimator (\ref{par:fisherest}) with $\bb{M}$ measured with and without the Born approximation. The difference is shown in units of the estimator standard deviation. We show the trend for $\Omega_m$ (blue), $w_0$ (red) and $\sigma_8$ (green).}
\label{fig:parbiasSN}
\end{figure}

@@

\subsection{Parameter bias}
When using forward models based on the Born approximation to fit observations, parameter bias may occur if the forward model is not accurate enough. We studied if this is the case by simulating 1000 LSST--like observations in which the convergence field $\kappa(\pt)$ is constructed using the full ray--tracing procedure. We used the Born approximation to fit these mock observations using the Fisher parameter estimator in eq.~(\ref{par:fisherest}). The results are shown in Figure \ref{fig:parbias}. We also studied how our conclusions are influenced by the survey angular galaxy density $n_g$, which controls the amplitude of the shape noise in the $\kappa$ reconstruction. The scaling of the power spectrum--induced parameter bias with $n_g$ is shown in Figure \ref{fig:parbiasSN}.

@@

Figure \ref{fig:psResiduals} shows a comparison between the Born--approximated $\kappa$ power spectra and the ones obtained with full ray--tracing, separating different orders in $\Phi$. We can conclude that the dominant contributions to the residuals come from the Born--geodesic cross power, which dominates the Born--lens--lens cross power by two orders of magnitude on small scales. Figure \ref{fig:skResiduals} shows that the geodesic and lens--lens contributions to the $\kappa$ skewness and kurtosis are comparable and that the lowest non--trivial post--Born corrections can fully account for the discrepancy between the Born--approximated quantities and the fully ray--traced ones. The geodesic and lens--lens corrections to the skewness we find agree, as orders of magnitude, with the ones already published in \citep{WLBispectrumDodelson}, although our measured reduced shear correction is larger. We stress, however, that our estimates and the ones in \citep{WLBispectrumDodelson} have been produced under different assumptions, in particular \citep{WLBispectrumDodelson} use a fully analytical approach based on the Limber approximation, different form forms for the smoothing windows and use their own assumptions for the form of the $\kappa$ bi--spectrum. Figs. \ref{fig:psResiduals} and \ref{fig:skResiduals} indicate that truncating $\kappa$ at $O(\Phi^2)$ post--Born terms, leads to inaccurate predictions of the power spectrum and moments. In particular, higher-order terms involving $\langle \kappa_{\rm born}^n \kappa_{\rm ll}^m \kappa_{\rm geo}^2\rangle$ and higher, cause large deviations (as seen by the difference between the solid and dashed green curves) that, in an exact approach, are canceled by $O(\Phi^3)$ corrections to $\kappa$, as pointed out by \citep{HirataKrause,CMBPrattenLewis,ScoccimarroLoop}. Therefore, in practice, in order to go beyond Born approximation, it is more advantageous, both for accuracy and for CPU time, to perform full ray--tracing (whose computational cost is comparable to those of the $O(\Phi^2)$ line--of--sight integrals; Table \ref{tab:benchmarks}).

@@

Figure \ref{fig:pdfMoments} shows the PDF of the 9 $\kappa$ moments defined in eq.~(\ref{par:moments}) over 1000 realizations of an LSST--like survey. This figure clearly shows that, while the Born approximation is a good predictor of the quadratic moments $\pmb{\mu}_2$ within one standard deviation, the higher moments $\pmb{\mu}_3,\pmb{\mu}_4$ show 2 to 3$\sigma$ deviations from their Born--approximated counterparts. This can lead to parameter bias when fitting observations. Figure \ref{fig:parbias} studies this possibility and shows that the Born approximation is sufficient to fit cosmology with the power spectrum of an LSST--like survey, with the result holding also for galaxy densities as high as $60\,{\rm galaxies/arcmin}^2$, as can be seen in Figure \ref{fig:parbiasSN}. The accuracy requirements, however, might be stricter for deeper surveys, such as Euclid \citep{Euclid}, which requires systematic effects not to be greater than $\sigma/3$. While the Born approximation is accurate in predicting the $\kappa$ power spectrum, the same is not true for higher order $\kappa$ moments. We have previously shown that these moments contain significantly more information than the power spectrum \citep{MinkPetri}, an expectation that was confirmed when fitting CFHTLenS data~\citep{CFHTMink}. The middle and bottom row of panels in Figure \ref{fig:parbias} show that indeed the constraints from the moments are $\approx$ 2 times tighter than from the power spectrum (seen by the narrow widths of the PDFs). As a result, highly significant biases are observed when fitting an observation with Born--approximated $\kappa$ moments. Although the presence of Gaussian galaxy shape noise reduces the significance of this bias, it cannot completely eliminate it, as higher order moments are sensitive to non--Gaussian statistical information in $\kappa$ images. 
These results lead us to the conclusion that the Born approximation is sufficient for future WL analyses that use the $\kappa$ power spectrum to constrain cosmology. This approach also has the advantage of being 4 times computationally faster than full ray--tracing, as we show in Table \ref{tab:benchmarks} for a selected reference test case. When considering higher order moments of $\kappa$, however, full ray--tracing is required in order to obtain unbiased constraints.

@@

\begin{itemize}
\item The lowest--order post--Born corrections to the convergence power spectrum, skewness and kurtosis are sufficient to fully account for the discrepancies between ray--tracing and the Born approximation.
\item Using the \ttt{LensTools} software package, Born integration costs 4 times less than ray--tracing, and consumes about half as much memory.
\item The Born approximation for the $\kappa$ power spectrum leads to negligible parameter bias for an LSST--like survey, and holds for survey galaxy densities as high as $60\,{\rm galaxies/arcmin^2}$.
\item Fitting an observation with Born--approximated higher $\kappa$ moments leads to significant bias in the $(\Omega_m,w_0,\sigma_8)$ triplet, even in the presence of galaxy shape noise.    
\end{itemize}
%
In this work we examined the validity of the Born approximation for WL galaxy surveys, but a similar study could in principle be carried for the lensing potential reconstruction from CMB temperature and polarization data \citep{CMBCalabrese}. Lensing of the CMB probes structures over a wider range of redshifts and hence CMB lensing observables can be expected to closer to Gaussian than their galaxy lensing counterparts. This suggests the possibility that non--Gaussian features in CMB lensing data could come from post--Born corrections of $O(\Phi^2)$ rather than from intrinsic non--Gaussianity in the Born $O(\Phi)$ terms. This possibility has been suggested by \citep{CMBPrattenLewis}, who looked at the CMB lensing $\kappa$ bi--spectrum. Because of the high significance with which non--Gaussianity in the CMB lensing potential can be detected with future Stage IV experiments \citep{CMBLNG}, we propose to investigate post--Born corrections to CMB lensing observables in future work.

@@

\section*{Acknowledgments}
We thank Uro\v{s} Seljak and Colin Hill for useful discussions. The $N$--body simulations in this work were performed at National Energy Research Scientific Computing Center (NERSC). We thank the LSST Dark Energy Science Collaboration (DESC) for the allocation of time. The ray--tracing simulations and parameter estimation calculations were performed at the NSF XSEDE facility, supported by grant number ACI-1053575, and at the New York Center for Computational Sciences, a cooperative effort between Brookhaven National Laboratory and Stony Brook University, supported in part by the State of New York. This work was supported in part by the U.S. Department of Energy under Contract No. DE-SC00112704, the NSF Grant No. AST-1210877 (to Z.H.), the Research Opportunities and Approaches to Data Science (ROADS) program at the Institute for Data Sciences and Engineering at Columbia University (to Z.H.) and a Simons Fellowship in Theoretical Physics (to Z.H.).

>>>>

\begin{abstract}
Accurate forward modeling of weak lensing (WL) observables from cosmological parameters is necessary for upcoming galaxy surveys. Because WL probes structures in the non--linear regime, analytical forward modeling is very challenging, if not impossible. Numerical simulations of WL features rely on ray--tracing through the outputs of $N$--body simulations, which requires knowledge of the gravitational potential and accurate solvers for light ray trajectories. A less accurate procedure, based on the Born approximation, only requires knowledge of the density field, and can be implemented more efficiently and at a lower computational cost. In this work, we use simulations to show that deviations of the Born--approximated convergence power spectrum, skewness and kurtosis from their fully ray--traced counterparts are consistent with the smallest non--trivial $O(\Phi^3)$ post--Born corrections (so-called geodesic and lens-lens terms). Our results imply a cancellation among the larger $O(\Phi^4)$ (and higher order) terms, consistent with previous analytic work. We also find that cosmological parameter bias induced by the Born approximated power spectrum is negligible even for an LSST--like survey, once galaxy shape noise is considered. When considering higher order statistics such as the $\kappa$ skewness and kurtosis, however, we find significant bias of up to 2.5$\sigma$. Using the \ttt{LensTools} software suite, we show that the Born approximation saves a factor of 4 in computing time with respect to the full ray--tracing in reconstructing the convergence.       
\end{abstract}

@@

\caption{CPU time and memory usage benchmarks for the convergence reconstruction operations. The test case we refer to in this table matches the specifications of the simulations used in this work. We we divide the line of sight in $N_l=42$ uniformly spaced lenses between the observer and the sources at $z_s=2$, each with a resolution of $4096^2$ pixels. The $\kappa$ field is resolved with $2048^2$ light rays. We show both the runtime for producing a single field of view and the CPU hours needed to perform the reconstruction 1000 times, to mock an LSST--like galaxy survey. Run times do not include the Poisson solution calculation, as this can be recycled to produce multiple field of view realizations. The Poisson solution run time is negligible in the account of the total CPU time needed for the production of $N_r\gg N_l$ field of view realizations.}
\label{tab:benchmarks}

@@

\begin{figure*}
\begin{center}
\includegraphics[scale=0.4]{Figures/csample.eps}
\end{center}
\caption{Sample convergence outputs for one realization of a $(3.5\,{\rm deg})^2$ field, with source galaxies at redshift $z_s=2$. The figure shows the convergence profile (top left), along with the Born approximation residuals (top right), the lens-lens post--Born contribution (bottom left) and the geodesic contribution (bottom right). The images have been smoothed with a Gaussian kernel of size $\theta_G=0.5\,{\rm arcmin}$.  Note the different scales in the bottom panels: the geodesic term (right), is over an order of magnitude larger than the lens--lens term (left), and is comparable in level and detailed structure to the full residual (top right). The ``22'' and ``33'' post--Born corrections to the $\kappa$ power spectrum, which are widely mentioned in the literature \citep{HirataKrause} are not directly observable from these $\kappa$ images.} 
\label{fig:csample}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics[scale=0.45]{Figures/powerResiduals.eps}
\end{center}
\caption{Contributions at different $\Phi$ orders to the $\kappa$ power spectrum: the left panel shows the auto power spectra $P_{\rm born,born}$ ($O(\Phi^2)$) and $P_{\rm ll},P_{\rm geo}$ ($O(\Phi^4)$). The right panel shows the residuals between the power spectrum of the full ray--traced $\kappa$ field and the one obtained with the Born approximation. For reference, we show the shape noise contributions (black dashed) and the first non--trivial reduced shear corrections to $P^{\kappa\kappa}$ (black solid), which can be both added to the forward models after the line of sight integration. We also show as an orange line the level of cosmic variance for the power spectrum expected in a LSST--like survey. Gaussian convolution effects with a window of size $\theta_G=0.5\,{\rm arcmin}$ are included. The residuals are compared to the two $O(\Phi^3)$ terms $2P_{\rm born,ll},2P_{\rm born,geo}$. The quantities shown are the ensemble averages over 8192 realizations of $\kappa$ in the fiducial cosmology $\bb{p}_0$.}
\label{fig:psResiduals}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics[scale=0.45]{Figures/bias_ngal_convergence_powerSN_s0_nb100.eps} \includegraphics[scale=0.45]{Figures/bias_ngal_convergence_momentsSN_s50_nb9.eps}
\end{center}
\caption{Parameter bias, obtained from the $\kappa$ power spectrum (left panel) and the $\kappa$ moments (right panel), as a function of the galaxy density angular $n_g$ used to compute the shape noise rms in eq. (\ref{par:shaperms}). The plotted quantity is the difference between the mean of 1000 parameter fits using the estimator (\ref{par:fisherest}) with $\bb{M}$ measured with and without the Born approximation. The difference is shown in units of the estimator standard deviation. We show the trend for $\Omega_m$ (blue), $w_0$ (red) and $\sigma_8$ (green). The quoted $\sigma_{\rm ray}$ is calculated as a standard deviation. Parameter estimates PDFs are not Gaussian because the estimator $\hat{\mathbf{d}}_{\rm obs}$ which appears in equation (\ref{par:fisherest}) in general is non--Gaussian distributed. When we average over multiple fields of view though (this is the case for LSST), the Gaussianity assumption is justified by the central limit theorem. This is why the standard deviation $\sigma_{\rm ray}$ is a reasonable benchmark for statistical significance.}
\label{fig:parbiasSN}
\end{figure*}

@@

\subsection{Parameter bias}
When using forward models based on the Born approximation to fit observations, parameter bias may occur if the forward model is not accurate enough. We studied if this is the case by simulating 1000 LSST--like observations in which the convergence field $\kappa(\pt)$ is constructed using the full ray--tracing procedure. We used the Born approximation to fit these mock observations using the Fisher parameter estimator in eq.~(\ref{par:fisherest}). The results are shown in Figure \ref{fig:parbias}. We also studied how our conclusions are influenced by the survey angular galaxy density $n_g$, which controls the amplitude of the shape noise in the $\kappa$ reconstruction. The scaling of the bias induced by the Born approximation on the power spectrum and $\kappa$ moments as a function of $n_g$ is shown in Figure \ref{fig:parbiasSN}.

@@

Figure \ref{fig:psResiduals} shows a comparison between the Born--approximated $\kappa$ power spectra and the ones obtained with full ray--tracing, separating different orders in $\Phi$. We can conclude that the dominant contributions to the residuals come from the Born--geodesic cross power, which dominates the Born--lens--lens cross power by two orders of magnitude on small scales. The dashed blue line in Figure \ref{fig:psResiduals} corresponds to the residuals $P_{\rm ray} - P_{\rm born} - 2P_{\rm born,ll} - 2P_{\rm born,geo}$, which are comparable to the $O(\Phi^3)$ terms themselves. This means that the $O(\Phi^4)$ post--Born terms are completely overshot by cosmic variance and numerical noise in this case. Figure \ref{fig:skResiduals} shows that the geodesic and lens--lens contributions to the $\kappa$ skewness and kurtosis are comparable and that the lowest non--trivial post--Born corrections can fully account for the discrepancy between the Born--approximated quantities and the fully ray--traced ones. The geodesic and lens--lens corrections to the skewness we find agree, as orders of magnitude, with the ones already published in \citep{WLBispectrumDodelson}, although our measured reduced shear correction is larger. We stress, however, that our estimates and the ones in \citep{WLBispectrumDodelson} have been produced under different assumptions. In particular, \citep{WLBispectrumDodelson} use a fully analytical approach based on the Limber approximation, they consider different smoothing window functions and use their own assumptions for the bi--spectrum of $\kappa$. Figs. \ref{fig:psResiduals} and \ref{fig:skResiduals} indicate that truncating $\kappa$ at $O(\Phi^2)$ post--Born terms, leads to inaccurate predictions of the power spectrum and moments. In particular, higher-order terms involving $\langle \kappa_{\rm born}^n \kappa_{\rm ll}^m \kappa_{\rm geo}^2\rangle$ and higher, cause large deviations (as seen by the difference between the solid and dashed green curves) that, in an exact approach, are canceled by $O(\Phi^3)$ corrections to $\kappa$, as pointed out by \citep{HirataKrause,CMBPrattenLewis,ScoccimarroLoop}. For example, regarding the skewness of $\kappa$, the residuals $\kappa^3_{\rm born+geo}-\kappa^3_{\rm born}$ contain terms up to order $O(\Phi^6)$. Some of these high order terms should be canceled by $O(\Phi^3)$ corrections to the $\kappa$ image. These cancellations do not show up if one truncates the expansion of $\kappa$ to $O(\Phi^2)$. This is the reason behind the discrepancy between the green curves in Figure \ref{fig:skResiduals}. Therefore, in practice, in order to go beyond Born approximation, it is more advantageous, both for accuracy and for CPU time, to perform full ray--tracing (whose computational cost is comparable to those of the $O(\Phi^2)$ line--of--sight integrals; Table \ref{tab:benchmarks}).

@@

Figure \ref{fig:pdfMoments} shows the PDF of the 9 $\kappa$ moments defined in eq.~(\ref{par:moments}) over 1000 realizations of an LSST--like survey. This figure clearly shows that, while the Born approximation is a good predictor of the quadratic moments $\pmb{\mu}_2$ within one standard deviation, the higher moments $\pmb{\mu}_3,\pmb{\mu}_4$ show 2 to 3$\sigma$ deviations from their Born--approximated counterparts. This can lead to parameter bias when fitting observations. Figure \ref{fig:parbias} studies this possibility and shows that the Born approximation is sufficient to fit cosmology with the power spectrum of an LSST--like survey, with the result holding also for galaxy densities as high as $60\,{\rm galaxies/arcmin}^2$, as can be seen in Figure \ref{fig:parbiasSN}. The accuracy requirements, however, might be stricter for deeper surveys, such as Euclid \citep{Euclid}, which requires systematic effects not to be greater than $\sigma/3$. While the Born approximation is accurate in predicting the $\kappa$ power spectrum, the same is not true for higher order $\kappa$ moments. We have previously shown that these moments contain significantly more information than the power spectrum \citep{MinkPetri}, an expectation that was confirmed when fitting CFHTLenS data~\citep{CFHTMink}. The middle and bottom row of panels in Figure \ref{fig:parbias} show that indeed the constraints from the moments are $\approx$ 2 times tighter than from the power spectrum (seen by the narrow widths of the PDFs). As a result, highly significant biases are observed when fitting an observation with Born--approximated $\kappa$ moments. Although the presence of Gaussian galaxy shape noise reduces the significance of this bias, it cannot completely eliminate it, as higher order moments are sensitive to non--Gaussian statistical information in $\kappa$ images. 
These results lead us to the conclusion that the Born approximation is sufficient for future WL analyses that use the $\kappa$ power spectrum to constrain cosmology. This approach also has the advantage of being 4 times computationally faster than full ray--tracing, as we show in Table \ref{tab:benchmarks} for a selected reference test case.

A few technical considerations are in order here. When adopting the Born approximation, it seems tempting to collapse all the particles in the $N$--body outputs in a single lens plane transverse to the line of sight, assigning to each particle a weight $W(\chi,\chi_s)$. Unfortunately the function $W$ is concave in $\chi$ and this ``single--lens--plane'' approach under--estimates $\kappa$ by a non--negligible amount. In order to avoid this concavity effect we need to use multiple discrete steps. We do not need to perform the full ray--tracing calculations however, but we can simply add the density values on the lens planes as light rays travel between them. The Born algorithm scales as $O(N_l)$. Ray--tracing has the same big $O$ complexity, but takes more time because at each step in the integration one needs to compute $O(N_R)$ second derivatives and $2\times 2$ matrix products, where $N_R$ is the number of light rays that resolve the $\kappa$ image. The quadratic corrections to $\kappa$ can also be computed in $O(N_l)$ when appropriate caching is used, but has a slightly different runtime compared to ray--tracing due to the different structure of the linear algebra operations involved. The memory usage is regulated by the number of two dimensional grids that need to be cached in order to perform the integration steps: in the Born case just a density grid is needed, but in the other cases one needs to keep track of the intermediate $\Phi$ derivatives as well.

When forward modeling higher order moments of $\kappa$ full ray--tracing is required in order to obtain unbiased constraints.

@@

\begin{itemize}
\item The post--Born corrections to the convergence power spectrum, skewness and kurtosis are well explained by the next--to--leading orders in the $\Phi$ expansion of each statistic. 
\item Using the \ttt{LensTools} software package, Born integration costs 4 times less than ray--tracing, and consumes about half as much memory.
\item The Born approximation for the $\kappa$ power spectrum leads to negligible parameter bias for an LSST--like survey, and holds for survey galaxy densities as high as $60\,{\rm galaxies/arcmin^2}$.
\item Fitting an observation with Born--approximated higher $\kappa$ moments leads to significant bias in the $(\Omega_m,w_0,\sigma_8)$ triplet, even in the presence of galaxy shape noise.    
\end{itemize}
%
In this work we examined the validity of the Born approximation for WL galaxy surveys, but a similar study could in principle be carried for the lensing potential reconstruction from CMB temperature and polarization data \citep{CMBCalabrese}. Lensing of the CMB probes structures over a wider range of redshifts and hence CMB lensing observables can be expected to closer to Gaussian than their galaxy lensing counterparts. This suggests the possibility that non--Gaussian features in CMB lensing data could come from post--Born corrections of $O(\Phi^2)$ rather than from intrinsic non--Gaussianity in the Born $O(\Phi)$ terms. This possibility has been suggested by \citep{CMBPrattenLewis}, who looked at the CMB lensing $\kappa$ bi--spectrum. Because of the high significance with which non--Gaussianity in the CMB lensing potential can be detected with future Stage IV experiments \citep{CMBLNG}, we propose to investigate post--Born corrections to CMB lensing observables in future work.

@@

\section*{Acknowledgments}
We thank the anonymous referee for the useful and insightful comments. We thank Uro\v{s} Seljak and Colin Hill for useful discussions. The $N$--body simulations in this work were performed at National Energy Research Scientific Computing Center (NERSC). We thank the LSST Dark Energy Science Collaboration (DESC) for the allocation of time. The ray--tracing simulations and parameter estimation calculations were performed at the NSF XSEDE facility, supported by grant number ACI-1053575, and at the New York Center for Computational Sciences, a cooperative effort between Brookhaven National Laboratory and Stony Brook University, supported in part by the State of New York. This work was supported in part by the U.S. Department of Energy under Contract No. DE-SC00112704, the NSF Grant No. AST-1210877 (to Z.H.), the Research Opportunities and Approaches to Data Science (ROADS) program at the Institute for Data Sciences and Engineering at Columbia University (to Z.H.) and a Simons Fellowship in Theoretical Physics (to Z.H.).
